Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-04-22 analysis/paper/paper.Rmd
sketch of results section

We ask whether colonial influence on indigenous populations can be detected in ornaments recovered from the archaeological record at Kiwulan (1400-1900 AD), a large Iron Age settlement in northeastern Taiwan.  Our hypothesis is that there was a greater diversity of ornaments types and materials at Kiwulan after European contact. We hypothesise that after Chinese contact there was a decline in the production, use and discard of ornaments at Kiwulan. We hypothesise that there is no change in the spatial distribution of ornaments at Kiwulan relating to these international contacts.

@@

Sketch of results section: 
H1
   1. We compare Raw material, shape/type and counts of ornaments in three time periods, and by spatial distribution 
   2.

>>>>

We ask whether colonial influence on indigenous populations can be detected in ornaments recovered from the archaeological record at Kiwulan (1400-1900 AD), a large Iron Age settlement in northeastern Taiwan.  Our hypothesis is that there was a greater diversity of ornaments types and materials at Kiwulan after European contact. We hypothesize that after Chinese contact there was a decline in the production, use and discard of ornaments at Kiwulan. We hypothesise that there is no change in the spatial distribution of ornaments at Kiwulan relating to these international contacts.

@@

Sketch of results section, should have some graphs and tables for these:

1. Overall summary of  Raw material, shape/type and counts of ornaments
2. Ornaments by: 
 - time period
 -- for each time period, spatial patterning
